Global optimization method with dual Lipschitz constant estimates for problems with non-convex constraints

### 2020-01-21 2019/NUMTA_Barkalov/Special Issure/article.tex
fix one misprint

	We will consider the initial problem (\ref{problem}) assuming that the problem functions $g_{j}(y), 1 \leq j \leq m+1$ may be defined only partly. It means that they are defined and calculable only in the sets 
\begin{equation}\label{D_sets}
	D_1 = D, \; D_{j+1} = \left\{ y \in D_j: \; g_j(y) \leq 0 \right\}, \; 1 \leq j \leq m.
\end{equation}
This situation is typical for the optimal design problems when some conditions for the functioning of the modeled object are not met and its other characteristics appear to be undefined. In this approach, the first violation of any constraint indicating that the point ybeing considered is no longer feasible terminates further computations at the point $y$.

>>>>

	We will consider the initial problem (\ref{problem}) assuming that the problem functions $g_{j}(y), 1 \leq j \leq m+1$ may be defined only partly. It means that they are defined and calculable only in the sets 
\begin{equation}\label{D_sets}
	D_1 = D, \; D_{j+1} = \left\{ y \in D_j: \; g_j(y) \leq 0 \right\}, \; 1 \leq j \leq m.
\end{equation}
This situation is typical for the optimal design problems when some conditions for the functioning of the modeled object are not met and its other characteristics appear to be undefined. In this approach, the first violation of any constraint indicating that the point $y$ being considered is no longer feasible terminates further computations at the point $y$.
